### 2018-07-08 methods.tex
reflected comments

The SaltProc tool is designed to expand SERPENT 2 depletion capabilities for modeling liquid-fueld \gls{MSR} for continuous reprocessing.
The Python package uses HDF5 \cite{the_hdf_group_hierarchial_1997} to store data, and the Nuclear Engineering Toolkit PyNE \cite{scopatz_pyne:_2012}
for SEPRENT output file parsing and nuclide naming. It is an open-source tool that uses a semi-continuous approach to 
simulate continuous feeds and removals in the \gls{MSR}.

The tool structure and capabilities of SaltProc are similar to ChemTriton tool for SCALE developed in \gls{ORNL} \cite{powers_new_2013}.
SaltProc is coupled with Monte Carlo SERPENT 2 software which allows to simulate online reprocessing for irregular full-core geometry with high level of fidelity.  The primary function of SaltProc is to manage material streams while SERPENT 2 performs most of the computationally heavy work, namely neutron transport and depletion calculations. Each material stream represents a fluid in the core design and has specific parameters (e.g. isotopic composition, reprocessing interval, mass rate, removal efficacy, etc). In addition, SaltProc provides a set of functions for each stream: read and write isotopic data in/from database, separate out specific isotopes from stream with defined efficiency, feed in specific isotopes to stream, and maintain constant number density of specific nuclide in the core. These attributes and functions are crucial to simulate the operation of a complex, multi-zone, multi-fluid \gls{MSR} and are universal for myriad reactor systems.

Figure~\ref{fig:saltproc_flow} illustrates the  online reprocessing simulation algorithm the coupled SaltProc and SERPENT 2. To perform a depletion step,
SaltProc reads an external SERPENT 2 template file which is defined by the user. This file contains input cards with parameters such as geometry,
moderator and construction materials isotopic composition, neutron population, criticality cycles, total heating power, and boundary conditions.
After the depletion calculation, SaltProc reads the depleted fuel composition file (\texttt{.bumat1}) and stores the depleted
composition isotopic vector in an HDF5 database. SaltProc only stores and edits the isotopic composition of the fuel stream,
which makes SaltProc a flexible tool to model any geometry: an infinite medium, a unit cell, a multi-zone simplified assembly, or a full core.
This flexibiliity allows the user to perform simulations of varying fidelity and computational intensity.

>>>>

The SaltProc tool \cite{andrei_rykhlevskii_arfc/saltproc:_201*} is designed to expand SERPENT 2
 depletion capabilities for modeling liquid-fueled \gls{MSR} for continuous reprocessing.
The Python package uses HDF5 \cite{the_hdf_group_hierarchial_1997} to store data, and the Nuclear Engineering Toolkit PyNE \cite{scopatz_pyne:_2012}
for SEPRENT output file parsing and nuclide naming. It is an open-source tool that uses a semi-continuous approach to 
simulate continuous feeds and removals in the \gls{MSR}.

The tool structure and capabilities of SaltProc are similar to ChemTriton tool for SCALE
developed in \gls{ORNL} \cite{powers_new_2013}. SaltProc is coupled with Monte Carlo SERPENT 2
software which allows to simulate online reprocessing for irregular full-core geometry with 
high level of fidelity.  The primary function of SaltProc is to manage material streams while
SERPENT 2 performs most of the computationally heavy work, namely neutron transport and depletion
calculations. Saltproc is defined as a 
python class, where each material stream is defined as a isotopic atomic density
vector variable. This allows tracking of time-sensitive material streams such as the
Pa-233 tank in the \gls{MSBR}. The user can define the reprocessing parameters, such as the 
reprocessing interval and removal efficiency.  In addition, SaltProc provides a set of functions 
for each stream: read and write isotopic data in/from database, separate out specific isotopes 
from stream with defined efficiency, feed in specific isotopes to stream, and maintain constant 
number density of specific nuclide in the core. These attributes and functions are crucial to 
simulate the operation of a complex, multi-zone, multi-fluid \gls{MSR} and are universal for 
myriad reactor systems.

Saltproc is currently in active development in Github, and has unit tests and
Travis continuous integration for sustainable development. There is also documentation
generated through Sphinx document generator for ease of use. We plan to implement
user-defined reprocessing scheme definition, two-region \gls{MSR} modeling capabilities,
and decay modeling in future releases.

Figure~\ref{fig:saltproc_flow} illustrates the  online reprocessing simulation algorithm the 
coupled SaltProc and SERPENT 2. To perform a depletion step,
SaltProc reads an external SERPENT 2 template file which is defined by the user. This file 
contains input cards with parameters such as geometry,
moderator and construction materials isotopic composition, neutron population, criticality 
cycles, total heating power, and boundary conditions.
After the depletion calculation, SaltProc reads the depleted fuel composition file (\texttt{
.bumat1}) and stores the depleted
composition isotopic vector in an HDF5 database. SaltProc only stores and edits the isotopic 
composition of the fuel stream,
which makes SaltProc a flexible tool to model any geometry: an infinite medium, a unit cell, a 
multi-zone simplified assembly, or a full core.
This flexibiliity allows the user to perform simulations of varying fidelity and computational 
intensity.
